A Data-Driven Framework for Neural Field Modelling

### 2010-10-28 ltx/first_order_framework/LaTeX_Manuscript.tex
added kernel estimates
updated histograms

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Graph/pdf/Figure7.pdf}
\end{center}
\caption{{\bf Histograms of the parameter estimates over 100
realisations}. The solid lines show the actual values of the parameters and the dotted lines show the means of the estimated parameters. (\textbf{A}) The histogram of the $\xi$ estimates where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant. (\textbf{B}) The histogram of the central excitatory connectivity kernel basis function parameter estimates, $\theta_0$. (\textbf{C}) The histogram of the surround inhibition connectivity kernel basis function parameter estimates, $\theta_1$. (\textbf{D}) The histogram of the longer range excitatory connectivity kernel basis function parameter estimates, $\theta_2$.}
\label{fig:Figure7}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Graph/pdf/Figure8.pdf}
\end{center}
\caption{{\bf Cross-section of connectivity kernel estimate}. The actual kernel is shown by the solid line, the mean kernel estimate (over 100 realisations) is shown by the dotted line and the 95~\% confidence interval is shown by the shaded grey region.}
\label{fig:Figure8}
\end{figure}

>>>>

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Graph/pdf/Figure7.pdf}
\end{center}
\caption{{\bf Histograms of the parameter estimates over 150
realisations}. The solid lines show the actual values of the parameters and the dotted lines show the means of the estimated parameters. (\textbf{a}) The histogram of the $\xi$ estimates where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant. (\textbf{b}) The histogram of the central excitatory connectivity kernel basis function parameter estimates, $\theta_0$. (\textbf{c}) The histogram of the surround inhibition connectivity kernel basis function parameter estimates, $\theta_1$. (\textbf{d}) The histogram of the longer range excitatory connectivity kernel basis function parameter estimates, $\theta_2$.}
\label{fig:Figure7}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Graph/pdf/Figure8_1.pdf}
\end{center}
\caption{{\bf Cross-section of connectivity kernel estimate}. The actual kernel is shown by the solid line, the mean kernel estimate (over 100 realisations) is shown by the dotted line and the 95~\% confidence interval is shown by the shaded grey region.}
\label{fig:Figure8}
\end{figure}
